---
title: "course-modes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE, 
                      message = FALSE)
```

```{r load-packages}
library(tidyverse)
```

```{r load-data}
modes <- readr::read_csv('data/Course_Modes_Coding - Sheet1.csv')
```

```{r}
modes
```

### Data cleaning

```{r, include = FALSE}
newmodes <- modes %>% 
  mutate(fall_online = `online (fall)`,
         fall_hybrid = `hybrid (fall)`,
         fall_person = `in-person (fall)`,
         spring_online = `online (spring)`,
         spring_hybrid = `hybrid (spring)`,
         spring_person = `in-person (spring)`,
         college = `trinity/pratt`,
         mmcn = `major/minor/cert/none`,
         degree = `BS/BA/both`)
```

```{r}
newmodes <- newmodes %>% 
  mutate(
    per_fall_online = ((fall_online)/((fall_online) + 
                                                 (fall_hybrid) + 
                                                 (fall_person))),
    per_fall_hybrid = ((fall_hybrid)/((fall_online) + 
                                                 (fall_hybrid) + 
                                                 (fall_person))),
    per_fall_person = ((fall_person)/((fall_online) + 
                                                 (fall_hybrid) + 
                                                 (fall_person))),
    per_spring_online = ((spring_online)/((spring_online) + 
                                                 (spring_hybrid) + 
                                                 (spring_person))),
    per_spring_hybrid = ((spring_online)/((spring_online) + 
                                                 (spring_hybrid) + 
                                                 (spring_person))),
    per_spring_person = ((spring_online)/((spring_online) + 
                                                 (spring_hybrid) + 
                                                 (spring_person)))
    )

```

```{r}
newmodes
```

### Analysis

- percent online, hybrid, in person for every subject

- percent online, hybrid, in person for every subject affiliated w a dept

- percent online, hybrid, in person for every subject that's ROTC

- fall vs. spring for ROTC

- percent online, hybrid, in person for every subject that's a major

- percent online, hybrid, in person for every subject that's not a major

- percent online, hybrid, in person for every subject that's a BA

- percent online, hybrid, in person for every subject that's a BSE

- percent online, hybrid, in person for every subject that's both (BA/BS)

- fall vs. spring for languages


